Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
add code for removing require

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] Code.scala:51:3: Could not extract tree in class: scala.this.Predef
             .require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(
             -9223372036854775808L)), "Number was too small for a int64, got: "
             .+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying >= -9223372036854775808L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [Warning ] Code.scala:53:3: Could not extract tree in class: scala.this.Predef
             .require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(
             9223372036854775807L)), "Number was too big for a int64, got: "
             .+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying <= 9223372036854775807L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [ Error  ] checkResult$0 depends on missing dependencies: require$1.
\end{lstlisting}

@@

>>>>

Stainless output:
\begin{lstlisting}[style=stainless]
  [Warning ] number/NumberType.scala:9:3: Could not extract tree in class: type A = BigInt (class scala.reflect.internal.Trees$TypeDef)
            type A = BigInt
            ^^^^^^^^^^^^^^^
  [Warning ] number/NumberType.scala:71:3: Could not extract tree in class: scala.this.Predef.require(Int64Impl.this.underlying.>=(math.this.BigInt.long2bigInt(-9223372036854775808L)), "Number was too small for a int64, got: ".+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying >= -9223372036854775808L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [Warning ] number/NumberType.scala:73:3: Could not extract tree in class: scala.this.Predef.require(Int64Impl.this.underlying.<=(math.this.BigInt.long2bigInt(9223372036854775807L)), "Number was too big for a int64, got: ".+(Int64Impl.this.underlying)) (class scala.reflect.internal.Trees$Apply)
            require(underlying <= 9223372036854775807L,
            ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^...
  [ Error  ] checkResult$0 depends on missing dependencies: require$1.

@@

Before:
\begin{lstlisting}[style=scala]
private case class Int64Impl(underlying: BigInt) extends Int64 {
  require(underlying >= -9223372036854775808L,
    "Number was too small for a int64, got: " + underlying)
  require(underlying <= 9223372036854775807L,
    "Number was too big for a int64, got: " + underlying)
}
\end{lstlisting}

After:
\begin{lstlisting}[style=scala]
private case class Int64Impl(underlying: BigInt) extends Int64 {
  require(underlying >= -9223372036854775808L)
  require(underlying <= 9223372036854775807L)
}
\end{lstlisting}

  /**
    * Checks if the given result is within the range
    * of this number type
    */
  private def checkResult(result: BigInt): A = {
    require(
         result <= BigInt("9223372036854775807")
      && result >= BigInt("-9223372036854775808"),
      "Result was out of bounds, got: " + result)
    result
  }
}
\end{lstlisting}

  /**
    * Checks if the given result is within the range
    * of this number type
    */
  private def checkResult(result: BigInt): A = {
    require(
          result <= BigInt("9223372036854775807")
      && result >= BigInt("-9223372036854775808"))
    result
  }
}
\end{lstlisting}
